\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-21 papers/jss/article.Rnw
Comment out the OpenCPU section about generating R objects from within Python.  This code could be added to OpenCPU docs somewhere, but it is confusing in an article about RProtoBuf because it doesn't at all look language neutral as we describe many times here.
It was a good addition before we had any python code in the Histogram
application section, but now we have a more concise and clear example
of python <-> R protocol buffer usage, so we don't need this any more.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@809 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

OpenCPU also provides a lot of meta-functionality such as handling
of sessions, exceptions, security, and more. OpenCPU also makes it possible to store
output of a function call on the server, instead of directly retrieving it. Thereby 
objects can be shared with other users or used as arguments in a subsequent
function call. But in its essence, the HTTP API provides a simple way to perform remote 
R function calls over HTTPS. The same request can be performed in Python as demonstrated
below. The code is a bit verbose because to show how the REXP message is created from 
scratch. In practice would probably write a function or small module construct a Protocol
Buffer message representing an R list from a Python dictionary object.

\begin{verbatim}
import urllib2;
from rexp_pb2 import *;

#create the post payload, i.e. list(n=42, mean=100)
payload = REXP(
  rclass = 5,
    rexpValue = [
      REXP(rclass = 2, realValue = [42]), 
      REXP(rclass = 2, realValue = [100])
    ],
    attrName = [
      "names"
    ],
    attrValue = [
      REXP(rclass = 0, stringValue = [STRING(strval="n"), STRING(strval="mean")])
    ]
);

#HTTP POST
req = urllib2.Request(
  "https://public.opencpu.org/ocpu/library/stats/R/rnorm/pb", 
  data = payload.SerializeToString(), 
  headers = {
    'Content-type': 'application/x-protobuf'
  }
)
res = urllib2.urlopen(req);

#parse output pb
msg = REXP();
msg.ParseFromString(res.read());

#the return value is a double vector in this case
print(msg.realValue);
\end{verbatim}

%\section{Application: Sending/receiving Interaction With Servers}
%
%Combined
%with an RPC system this means that one can interactively craft request
%messages, send the serialized message to a remote server, read back a
%response, and then parse the response protocol buffer interactively.

%TODO(mstokely): Talk about Jeroen Ooms OpenCPU, or talk about Andy
%Chu's Poly.

>>>>

% OpenCPU also provides a lot of meta-functionality such as handling
% of sessions, exceptions, security, and more. OpenCPU also makes it possible to store
% output of a function call on the server, instead of directly retrieving it. Thereby 
% objects can be shared with other users or used as arguments in a subsequent
% function call.
%  But in its essence, the HTTP API provides a simple way to perform remote 
% R function calls over HTTPS. The same request can be performed in Python as demonstrated
% below. The code is a bit verbose because to show how the REXP message is created from 
% scratch. In practice would probably write a function or small module construct a Protocol
% Buffer message representing an R list from a Python dictionary object. 
%
% \begin{verbatim}
% import urllib2;
% from rexp_pb2 import *;
%
% #create the post payload, i.e. list(n=42, mean=100)
% payload = REXP(
%  rclass = 5,
%    rexpValue = [
%      REXP(rclass = 2, realValue = [42]), 
%      REXP(rclass = 2, realValue = [100])
%    ],
%    attrName = [
%      "names"
%    ],
%    attrValue = [
%      REXP(rclass = 0, stringValue = [STRING(strval="n"), STRING(strval="mean")])
%    ]
%);
%
%#HTTP POST
%req = urllib2.Request(
%  "https://public.opencpu.org/ocpu/library/stats/R/rnorm/pb", 
%  data = payload.SerializeToString(), 
%  headers = {
%    'Content-type': 'application/x-protobuf'
%  }
%)
%res = urllib2.urlopen(req);
%        
%#parse output pb
%msg = REXP();
%msg.ParseFromString(res.read());
%
%#the return value is a double vector in this case
%print(msg.realValue);
%\end{verbatim}
